---
title: "FARS analysis package"
author: "Roland Krause"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

A fragment of a package to parse, munge and display data of the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System (FARS)
written for the Coursera course "Building R packages". The original website indicated
in the course is no longer accessible, hence explantions for e.g. state IDs an
    
## Data
Data is not included in the package and needs to be downloaded from the course site. Unfortunately, the website 
to explain the data is no longer available. 

## Simple examples

The useful functions of this package are  `fars_map_state` and `fars_summarize_years`. Other functions merely provide basic funtionalities used by top-level functions. 


### Mapping accidents by state
`fars_map_state` will present an image of the location of accidents on a map of the state. 

```{r, eval=FALSE}

fars_map_state(48, 2014) 
```

### Summary by month

A simple breakdown by month of the respective years.

```{r eval=FALSE}
fars_summarize_years(2013)
```


### Internal functions

In principle, these functions provides only very basic routines. In a final package, they would probably not be exported
and include more resilience, e.g. for missing installation data etc. 

```{r eval=FALSE}
fars_file <- make_filename(2013)
fars_df <- fars_read(fars_file)
fars_simple_df <- fars_read_years(years)
```
