---
title: "FARS analysis package"
author: "Roland Krause"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


A fragment of a package to parse, munge and display data of the 
    US National Highway Traffic Safety Administration's Fatality Analysis Reporting System (FARS)
    written for the Coursera course "Building R packages".
    

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Data
Data is not included in the package and needs to be downloaded from the source site

## Mapping data

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## A simple examples

The really useful functions of this package are the functions `fars_map_state` and 

```{r, echo=FALSE, results='asis', eval=FALSE}

fars_map_state(48, 2014) 
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
